FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-19 NewVersion/sections/Formalization.tex
S3,S5 by Haoyuan

\textsc{(T-Invk)} is the typing rule for method invocation.
Naturally, the receiver and the arguments are required to be well-typed.
$\mbody$ is our key function for method lookup that implements the
hierarchical dispatching algorithm. The formal definition will be introduced in Section~\ref{sec:auxdefs}.
Here $\mbody(m, I_0, I_0)$ finds the most specific $m$ above $I_0$. ``Above $I_0$'' specifies
the search space: it not only includes the body of $I_0$, but also its super types.
For the general case, however, the hierarchical invocation $\mbody(m, I, J)$ finds ``the most specific $m$
above $I$ and along path/branch $J$''.\haoyuan{Make sure we mentioned this in Overview.}

@@

\subsection{Small-step Semantics and Congruence}
Figure~\ref{fig:smallstep} defines the small-step semantic and
congruence rules of \MIM{}. When evaluating an expression, they
are invoked recursively and alternately, and produce a single value in
the end. %\haoyuan{we need to be consistent on paragraph upper/lower case.}

>>>>

\textsc{(T-Invk)} is the typing rule for method invocation.
Naturally, the receiver and the arguments are required to be well-typed.
$\mbody$ is our key function for method lookup that implements the
hierarchical dispatching algorithm. The formal definition will be introduced in Section~\ref{sec:auxdefs}.
Here $\mbody(m, I_0, I_0)$ finds the most specific $m$ above $I_0$. ``Above $I_0$'' specifies
the search space, namely the super types of $I_0$ including itself.
For the general case, however, the hierarchical invocation $\mbody(m, I, J)$ finds ``the most specific $m$
above $I$ and along path/branch $J$''. ``Along path $J$'' additionally requires the result to relate to $J$, that is to say,
the most specific interface has a subtyping relationship with $J$.

@@

\subsection{Small-step Semantics and Congruence}
Figure~\ref{fig:smallstep} defines the small-step semantic and
congruence rules of \MIM{}. When evaluating an expression, they
are invoked recursively and produce a single value in
the end. %\haoyuan{we need to be consistent on paragraph upper/lower case.}
